Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study

### 2022-02-22 csmc_mume_2020/paper/JCMS_2021/paper.tex
Final JCMS changes

Target-based computer-assisted orchestration takes a target sound as an input and attempts to find instrumental samples that best match the target given a specific similarity metric and a set of constraints. A solution to this problem is a set of orchestral scores that represent the mixtures of audio samples in the database, ranked by similarity with the target sound. Valid orchestral scores may contain several instruments sounding simultaneously, selected out of a large number of possible combinations of sounds from the database.

@@

The choice of using the Mel spectrogram as input features for classification models is common in music information retrieval \cite{McKinney2003} and can be considered to be an appropriate representation of sound and musical signals. Such setup proved to be successful in \cite{Salamon17}. Specifically, the Mel spectrogram uses the Mel scale to create a perceptual representation of sound. Since we are attempting to recreate the timbre of a sound, and timbre is a perceptual descriptor, the Mel spectrogram is a fitting representation.

>>>>

Target-based computer-assisted orchestration takes a target sound as an input and attempts to find instrumental samples that best match the target given a specific similarity metric and a set of constraints. The target can be any arbitrary sound file, it does not have to be pitched, rhythmic, or ``musical'' in any way. A solution to this problem is a set of orchestral scores that represent the mixtures of audio samples in the database, ranked by similarity with the target sound. Valid orchestral scores may contain several instruments sounding simultaneously, selected out of a large number of possible combinations of sounds from the database.

@@

The Mel spectrogram is a representation of sound that mirrors the non-linear way in which humans perceive frequency, which makes it a perceptual representation of sound. Since we are attempting to recreate the timbre of a sound, and timbre is a perceptual descriptor, the Mel spectrogram is a fitting representation. It is common in music information retrieval \cite{McKinney2003} and has been successfully used in other tasks that employ neural networks for sound classification \cite{Salamon17}.
